### 2023-06-10 README.Rmd
230610_v123

> &#10071; <code>validateHOT</code> is currently just taking indexes instead of column names, please be aware of this. However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>. For example, if you want to find out the column index of <code>id</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.

@@

>>>>

> &#10071; <code>validateHOT</code> is currently just taking indexes instead of column names, please be aware of this. However, you can easily find out the index by using the <code>names()</code> function or by using <code>which()</code> and <code>colnames()</code>, both functions are provided by the base package [@base]. For example, if you want to find out the column index of <code>id</code>, we could also use <code>which(colnames(CBC) == "ID")</code>.

@@

In a second example, we again use a *CBC*, however, this time we show how to use <code>validateHOT</code> if one of the variables are linear coded. All other examples are provided in the Vignette.

We are using the data frame <code>CBC_lin</code> which is also provided by the <code>validateHOT</code> package. We first load the data frame.

```{r}
data("CBC_lin")
```

Next, we create the validation/ holdout task to evaluate it in the next step. We use a validation/ holdout task with three alternatives plus the *no-buy* option, just as we did in the previous example. The only difference to the previous example is that we coded the third attribute (<code>Att3_Lin</code>) as linear.

Again, we first define <code>data</code>. The <code>id</code> is saved in the first column. The utilities for the <code>None</code> parameter are stored in the 15th column, and we again set <code>prod</code> to 3 (**excluding** the *no-buy* alternative). Next, we define the <code>prod.levels</code> for each alternative. For example, we can see that the second see that the second alternative is composed of <code>Att1_Lev5</code>, <code>Att2_Lev4</code>, and <code>60</code> which is the value that should be interpolated. We can see that this value is the one that needs to be interpolated if we take a closer look at the <code>coding</code> argument. This tells us that the first two attributes (<code>Att1_Lev5</code>, <code>Att2_Lev4</code> in the case of alternative 2) are part-worth coded (<code>0</code>) while the third attribute is linear coded (<code>1</code>).

To interpolate the value, we have to provide <code>validateHOT</code> the <code>interpolate.levels</code>. These **need** to be the same as provided to, e.g., Sawtooth as levels. Moreover, it is important that the value that should be interpolated needs to lie within the lower and upper bound of <code>interpolate.levels</code>. In our case, we had 7 levels that range from 10 to 70. The value we want to interpolate for the second alternative is 40, which of course lies within 10 and 70.

Next, we define the column index of the linear coded variable (<code>lin.p</code>) and specify the <code>coding</code> we talked about above. Again, we are running a *CBC* specified by the <code>method</code> argument. This time, we would like to keep some of the variables to the data frame, which we specify in <code>varskeep</code>. We only keep one further variable, however, you can specify as many as you want. This could be relevant if you would like to display results per group. Finally, we just tell <code>validateHOT</code> the column index of the final choice (<code>choice</code>) and we are good to go.

```{r}
CBC <- createHOT(
  data = CBC_lin,
  id = 1,
  None = 15,
  prod = 3,
  prod.levels = list(c(4, 9, 60), c(8, 12, 40), c(5, 10, 45)),
  interpolate.levels = list(c(10, 20, 30, 40, 50, 60, 70)),
  lin.p = 14,
  coding = c(0, 0, 1),
  method = "CBC",
  varskeep = 17,
  choice = 16
)
```

The next steps are the same as above. However, let us take a look at some examples in which we display the results per group. Let us again begin with the <code>hitrate()</code> function. To do so, we specify the column index of the grouping variable in the <code>Group</code> argument.

```{r}
hitrate(data = CBC, id = 1, opts = c(2:5), Group = 6, choice = 7)
```

In this case, the Grouping variable is just an integer. However, the output is different if it is a factor or if it is labelled data. To proof this we just quickly change <code>Group</code> in a factor by using the <code>factor()</code> function provided by @base.

```{r}
CBC$Group <- base::factor(CBC$Group,
                          levels = c(1:3),
                          labels = paste0("Group_", c(1:3)))
```

Afterward, we display the *mean hit probability* by running the <code>mhp()</code> function.

```{r}
mhp(data = CBC, id = 1, opts = c(2:5), Group = 6, choice = 7)
```

For more examples, please see the accompanied vignette.
